NFC and burnout in teachers - A replication and extension study

### 2021-09-09 Manuscript/Manuscript.Rmd
changed column reference

  mbi <- data[,10:30]             # Maslach Burnout Inventory grep(‚ncs‘, colnames(data))
  erq <- data[,31:40]             # Emotion Regulation Questionnaire
  scs <- data[,41:53]             # Self Control Scale
  ws <- data[,54:90]              # Work Satisfaction
  ncs <- data[,c(91:98,100:107)]  # Need for Cognition Scale (without the dummy item)
  covb <- data[,108:118]          # Covid Burden Items
  dth <- ws[,c(4,8,9)]            # the Work Satisfaction items for the latent variable Demands Too High
  dtl <- ws[,c(12,26,27)]         # the Work Satisfaction items for the latent variable Demands Too Low
  drf <- ws[,c(17,21,24)]         # the Work Satisfaction items for the latent variable Demand-Resource-Fit

@@

    correlation_matrix <- function(df,
                                   type = "pearson",
                                   digits = 3,
                                   decimal.mark = ".",
                                   use = "all",
                                   show_significance = TRUE,
                                   replace_diagonal = FALSE,
                                   replacement = ""){
      # check arguments
      stopifnot({
        is.numeric(digits)
        digits >= 0
        use %in% c("all", "upper", "lower")
        is.logical(replace_diagonal)
        is.logical(show_significance)
        is.character(replacement)
      })
      # we need the Hmisc package for this
      require(Hmisc)

@@

  repli_model <- '
  # direct paths
    scs       ~   a1 * ncs + years
    erq_reap  ~   a2 * ncs
    erq_supp  ~   a3 * ncs
    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

@@

  # Make a path diagram to visualize the results
  # (This is just okay, it is not the final version, e.g. there is no path from NCS to MBI yet)

  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,0.5,-0.1,-0.4,0.2,0.2,0.5), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```

>>>>

  mbi <- data[,grep("MBI", colnames(data))]   # Maslach Burnout Inventory
  erq <- data[,grep("ERQ", colnames(data))]   # Emotion Regulation Questionnaire
  scs <- data[,grep("SCS", colnames(data))]   # Self Control Scale
  ws <- data[,grep("WS", colnames(data))]     # Work Satisfaction
  ncs <- data[,grep("NCS", colnames(data))]   # Need for Cognition Scale
  ncs <- ncs[,-9]                             # remove the dummy item
  covb <- data[,grep("COV", colnames(data))]  # Covid Burden Items
  dth <- ws[,c(4,8,9)]                        # the Work Satisfaction items for the latent variable Demands Too High
  dtl <- ws[,c(12,26,27)]                     # the Work Satisfaction items for the latent variable Demands Too Low
  drf <- ws[,c(17,21,24)]                     # the Work Satisfaction items for the latent variable Demand-Resource-Fit

@@

    correlation_matrix <- function(df,
                                   type = "spearman",
                                   digits = 3,
                                   decimal.mark = ".",
                                   use = "all",
                                   show_significance = TRUE,
                                   replace_diagonal = FALSE,
                                   replacement = ""){
      # check arguments
      stopifnot({
        is.numeric(digits)
        digits >= 0
        use %in% c("all", "upper", "lower")
        is.logical(replace_diagonal)
        is.logical(show_significance)
        is.character(replacement)
      })
      # we need the Hmisc package for this
      require(Hmisc)

@@

  repli_model <- '
  # direct paths
    scs       ~   a1 * ncs
    erq_reap  ~   a2 * ncs
    erq_supp  ~   a3 * ncs
    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

@@

  # Make a path diagram to visualize the results

  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```

```{r objective1years, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

  # Replication of Grass et al. (2018) using years spent teaching as a variable influencing self-control
  # (as indicated by the correlation of it with SCS but not with the other variables)

  repli_model_years <- '
  # direct paths
    scs       ~   a1 * ncs + y * years
    erq_reap  ~   a2 * ncs
    erq_supp  ~   a3 * ncs
    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

  # indirect effects
    Indirect1 := (a1 * b1) + (y * b1)
    Indirect2 := a2 * b2
    Indirect3 := a3 * b3

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3) + (y * b1)
'

  fityears <- sem(
    model = repli_model_years,
    data  = score_data,
    se = "bootstrap",
    bootstrap = 2000
  )

  fityears_summ <- summary(fityears, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE}

  # Make a path diagram to visualize the results

  fityears_plot <- semPaths(fityears, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```
